---
title: "README"
author: "Miles & [Teammate Name]"
output: 
  github_document:
  pandoc_args: ["--wrap=none"]
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# install.packages(c("tidyverse", "knitr", "kableExtra"))  # run once, then leave commented out
library(tidyverse)
library(knitr)
library(kableExtra)
```
# THIS IS A TEXT

### Frequency tables for categorical variables

```{r frequency-tables}
kable(hpi_master %>% count(hpi_type, sort = TRUE), caption = "Observations by hpi_type")
kable(hpi_master %>% count(hpi_flavor, sort = TRUE), caption = "Observations by hpi_flavor")
kable(hpi_master %>% count(level, sort = TRUE), caption = "Observations by Geography Level")
kable(hpi_master %>% count(frequency, sort = TRUE), caption = "Observations by Frequency")
```

### Visualization: distribution of index_nsa

```{r hist-index}
ggplot(hpi_master, aes(x = index_nsa)) +
  geom_histogram(bins = 50, fill = "steelblue", color = "white") +
  labs(title = "Distribution of Non-Seasonally-Adjusted HPI",
       x = "Index (NSA)", y = "Count") +
  theme_minimal()
```

### Visualization: index_nsa by hpi_type

```{r box-index-by-type}
ggplot(hpi_master, aes(x = hpi_type, y = index_nsa, fill = hpi_type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "HPI (NSA) by Index Type", x = NULL, y = "Index (NSA)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### Visualization: national HPI trend over time

```{r national-trend}
national_trend <- hpi_master %>%
  filter(place_id == "USA", hpi_type == "traditional", frequency == "monthly") %>%
  mutate(date = as.Date(paste(yr, period, "01", sep = "-")))

ggplot(national_trend, aes(x = date, y = index_nsa, color = hpi_flavor)) +
  geom_line(linewidth = 0.8) +
  labs(title = "U.S. National HPI Over Time (Traditional, Monthly)",
       x = NULL, y = "Index (NSA)", color = "Flavor") +
  theme_minimal()
```
  
  
  national_over_time <- hpi_master %>%
    filter(place_id == "USA",
           hpi_type == "traditional",
           hpi_flavor == "purchase-only",
           frequency == "monthly") %>%
    mutate(date = as.Date(paste(yr, period, "01", sep = "-")))
  
  ggplot(national_over_time, aes(x = date, y = index_nsa)) +
    geom_line(color = "steelblue", linewidth = 0.9) +
    labs(title = "U.S. National House Price Index Over Time",
         subtitle = "Traditional, Purchase-Only, Monthly (Not Seasonally Adjusted)",
         x = NULL, y = "Index (NSA, base = 100)") +
    theme_minimal()







## 3. Expanding Your Investment Knowledge

*(To do: identify and describe a complementary dataset.)*

## 4. Communicating Your Findings

*(To do: plain-language summary for a non-technical audience.)*
